Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
Various little bits of work

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{subcaption} % subfigures
\usepackage{float}

@@

Evaluating likelihood function requires that we compute a ``mock'' image from
the current setting of the parameters. This mock image is calculated using
standard ray-tracing methods with a uniform grid of $n \times n$ rays
fired per image pixel. However, certain kinds of proposals do not affect the
image in any way, such as those that change the noise parameters.

@@

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{horseshoe_image.pdf}
\caption{The g-band INT image of the Cosmic Horseshoe.
\label{fig:horseshoe_image}}
\end{center}
\end{figure}

@@

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). The posterior distribution for
$N_{\rm lens}$ also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures.\label{fig:simdata_masses}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens2.pdf}
\caption{\label{fig:N_lens2}}
\end{center}
\end{figure}

>>>>

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{subcaption} % subfigures
\usepackage{float}

@@

Evaluating likelihood function requires that we compute a ``mock'' image from
the current setting of the parameters. This mock image is calculated using
standard ray-tracing methods with a uniform grid of $n \times n$ rays
fired per image pixel. However, certain kinds of proposals do not affect the
image in any way, such as those which change the noise parameters. For efficiency
we do not recompute the mock image in these cases.

@@

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. The source redshift is $z_s=2.379$, and the
lens is a massive luminous red galaxy at $z_l=0.4457$.
Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{horseshoe_image.pdf}
\caption{The g-band INT image of the Cosmic Horseshoe, with the lens galaxy
subtracted.
\label{fig:horseshoe_image}}
\end{center}
\end{figure}

@@

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:simdata_masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). The posterior distribution for
$N_{\rm lens}$ also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures.\label{fig:masses2}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens2.pdf}
\caption{The posterior distribution for the number of lens substructures
in the Cosmic Horseshoe system. There is mild evidence in favour of the
hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens2}}
\end{center}
\end{figure}
